Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2016-01-20 manuscript/text_reuse.tex
updated intro

Research on public policy adoption and diffusion has conventionally relied on modest hand-coded datasets encode when one or a handful of policies were adopted by each jurisdiction \citep{boehmke2012}. Scholars of public policy diffusion have recently turned their attention to the empirical identification of emulation ties connecting policy jurisdictions \citep{volden2006,boehmke2009,desmarais2015,garrett2015}. Identifying instances of policy emulation and explicit diffusion ties opens policy diffusion scholarship to an entirely new set of questions and theories that can be approached empirically. In this paper we draw upon a massive and nearly all-encompassing source of data from which to infer diffusion ties -- the text of legislation. If the computer-based analysis of bill text can be tuned to successfully identify policy adoption and emulation, we will be able to vastly scale up both the scale of data gathered and the precision of diffusion inferences.

 How ever, it is not clear, how well text reuse is suited to to detect real policy diffusion. There are several complications that we are addressing in this paper. First, every bill has procedural content that is not related to the policy content of the bill. Since every state legislature has a set of such standard or boiler plate text in each bill, there will be significant text reuse between bills in the same state and possibly also between bills from different states. Second, it is not obvious how much text reuse will mean substantive policy overlap. Given that each bill pair has a continuous proportion of overlapping text, setting the threshold too low might mean to classify bills as equivalent that are only in the same policy area, or are on a similar issue, but are opposed in content. On the other hand, setting the threshold too high could mean overlooking equivalent bills because of small insignificant changes to the text. 
 In this paper we address these issues and evaluate how much policy overlap can be detected using text reuse measures. Following Wilkerson et al. (2015) we use supervised machine learning to separate boiler plate from substantive text. We further more use an original data set on policy diffusion to evaluate how much equivalent policy can be detected using measures of text reuse. Using the system developed by Burges et al. (2015) we calculate text reuse scores for all pairs of bills in our dataset.  
We will then assess the scientific value of the text reuse scores in several different ways. First, we use topic modeling on the discovered reused text sequences to assess the content of the matching text. Second, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills. Third, we assess the how well policy diffusion networks that have been established by previous research can be discovered using the amount of text reuse between states. And fourth, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.

@@

To evaluate whether text re-use corresponds to the transfer of policy, we test whether the presence of a diffusion network tie between two states is a predictor of text reuse. We use the policy diffusion networks inferred in \citet{desmarais2015}. We use [FL FILL IN] to measure the incidence of dyadic text alignment between all state bills covering the time period 200--[??]. For each bill, we first gather the 100 closest bills based on cosine similarity in the term vectors characterizing the bills. We then represent a dyad of bills by the text alignments between them. For each state-pair we calculate the number of alignments between bills from each state. The median number of alignments between states is 3,491 with a mean of 6,309 and standard deviation of 8,809. The ``Diffusion Ties'' variable measures the number of diffusion edges between states in the 2008 diffusion network, as measured by \citet{desmarais2015}. The number of diffusion edges between two states is either 0, 1, or 2. The diffusion network in 2008 is inferred using policy adoptions in the 35 years preceding (and excluding) 2008. As such, we do not risk double-counting bills in the policy adoption and text re-use data. There is one observation in the analysis for each of the 1,225 unique state-pairs. Since this is dyadic data, we use a matrix permutation method, quadratic assignment procedure, to calculate $p$-values \citep{krackhardt1988}. As a robustness check, we run the model with both the identity and log link.\footnote{The $p$-values were calculated using 5,000 random matrix permutations.}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
 & Coefficient & p-value & Coefficient & p-value \\ 
  \hline
Intercept & 5717.18 & 0.0000 & 8.0431 & 0.0000 \\ 
  Diffusion Ties & 2417.00 & 0.0308 & 0.3288 & 0.0452 \\ 
   \hline
\end{tabular}
\caption{Predicting number of alignments in legislation across states with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}

>>>>

The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}. Research on public policy adoption and diffusion has conventionally relied on modest hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}. In this paper we draw upon a massive and nearly all-encompassing source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures. We take an automated, computer-based, approach to the analysis of bill text. This vastly increases the volume of data that can be included in policy diffusion research.

Through the development of automated text-analytic methods of measuring policy diffusion we consider several methodological challenges and broader conceptual hurdles. The central methodological puzzles are two-fold. First, we need to extract the substantive text of the legislation---minimizing the affect of procedural text on our measures of text reuse. Second, we need to develop a method for quantitatively scoring the reused text between bills. The main conceptual puzzle with which we engage is the potential ambiguity regarding whether two policies should be considered the same for the purpose of policy diffusion research. We cannot define a standard in the literature according to which two policies can be deemed equivalent, and argue instead for conceptualizing policy diffusion in terms of a continuum of similar policy rather than a dichotomy of equivalence.

We take a multi-pronged approach to evaluating the performance of text reuse in measuring the consideration and adoption of similar laws. First, we use topic modeling on the discovered reused text sequences to assess the content of the matching text. Second, we investigate the relationship between the ideological distance of the legislators that proposed two bills and the text reuse scores between these bills. Third, we assess the how well policy diffusion networks that have been established by previous research can be predicted using the amount of text reuse between states. And fourth, we use data on equivalent bills collected by the National Council of State Legislatures to build an evaluation data set containing true policy overlap to assess the accuracy of text reuse in predicting policy overlap.

@@

To evaluate whether text re-use corresponds to the transfer of policy, we test whether the presence of a diffusion network tie between two states is a predictor of text reuse. We use the policy diffusion networks inferred in \citet{desmarais2015}. We use [FL FILL IN] to measure the incidence of dyadic text alignment between all state bills covering the time period 200--[??]. For each bill, we first gather the 100 closest bills based on cosine similarity in the term vectors characterizing the bills. We then represent a dyad of bills by the text alignments between them. For each state-pair we calculate the sum of the natural logs of the alignment scores. The ``Diffusion Ties'' variable measures the number of diffusion edges between states in the 2008 diffusion network, as measured by \citet{desmarais2015}. The number of diffusion edges between two states is either 0, 1, or 2. The diffusion network in 2008 is inferred using policy adoptions in the 35 years preceding (and excluding) 2008. As such, we do not risk double-counting bills in the policy adoption and text re-use data. There is one observation in the analysis for each of the 1,225 unique state-pairs. Since this is dyadic data, we use a matrix permutation method, quadratic assignment procedure, to calculate $p$-values \citep{krackhardt1988}. As a robustness check, we run the model with both the identity and log link.\footnote{The $p$-values were calculated using 5,000 random matrix permutations.}

\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Identity Link} & \multicolumn{2}{c}{Log Link} \\
  \hline
 & Coefficient & p-value & Coefficient & p-value \\ 
  \hline
Intercept & 21220.1435 & 0.0000 & 9.3643 & 0.0000 \\ 
  Diffusion Ties & 8551.8602 & 0.0352 & 0.3190 & 0.0494 \\ 
   \hline
\end{tabular}
\caption{Predicting number of alignments in legislation across states with diffusion ties. Coefficients calculated with OLS regression. $p$-values based on 5,000 QAP permuations.}
\label{tab:qap.diffusion}
\end{table}
